---
title: "Advanced visualization with ggplot2"
subtitle: "Challenge 2"
author: "YOUR NAME"
format: 
  html:
    self-contained: true
---

# Instructions

**Task:** Open up the New York Times article [A Summer of Strikes](https://www.nytimes.com/interactive/2023/09/03/business/economy/strikes-union-sag-uaw.html), and scroll down to the plot titled "Union membership has fallen sharply over the past four decades (Share of the work force in a union, by industry)".

Using `ggplot2` and other tools in R, recreate this plot. Note that you will need to create the data underlying the plot yourself. You can create this data in R with `tibble()`. You can also write the data in Excel or Google Sheets and export it as a CSV file.

**Requirements for passing:**

- Panels for "All workers", "By Sector", and "By Industry" are shown.
- Arrows showing the change from 1983 to 2022 are shown.
- The actual percentages in 1983 and 2022 are shown as text.
- X-axis tick marks are at 0, 25, and 50.
- Plot title says "Union membership has fallen sharply over the past four decades".
- Plot subtitle says "Share of the work force in a union, by industry".

**Submission:** Click the "Render" button in RStudio to knit a self-contained HTML will all images in embdeded. Commit and push changes to this file as well as the generated HTML. Create a **pull request** to submit your assignment by midnight on Monday 2/5.



# Setup

```{r}
# Code for loading packages
# And code for reading in data if using the Excel/Google Sheets-->CSV approach
```

```{r}
# Code for generating the data (if using the tibble() approach)
```




# Visualization


```{r}
# Code for recreating the visualization
# Use as many code chunks as you need to organize your work well
```




# AI usage

If you use an AI tool (e.g., ChatGPT, Google Bard) to help with this assignment, please paste below the prompts you use and their associated output

**Prompt:**

**Output:**

Keep in mind that the use of AI has a [huge energy cost](https://lmyint.github.io/212_spring_2024/syllabus.html#artificial-intelligence-ai-use). Please describe an energy-saving activity that you can start engaging in to offset this cost.

**Energy-saving activity:** 
